`traveltime`: an R package to calculate travel time across a landscape from user-specified locations

### 2025-05-02 paper/paper.qmd
Include Singapore open data licence acknowledgement
replace latex fig refs with rmardown ones AGAIN NB: this adds in the word Figure to the numeric reference so this word is deleted again. Bah

We present the resulting calculated travel times in Figure \ref{fig-result} where, as expected, the travel times are lowest near station exits (per Figure \ref{fig-data}) and progressively higher further away. Note that the results in `trave_time_singapore` include infinite values (`Inf` above). In Figure \ref{fig-data}, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in Figure \ref{fig-result}. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in Figure \ref{fig-result}.

@@

>>>>

We present the resulting calculated travel times in @fig-result where, as expected, the travel times are lowest near station exits (per @fig-data) and progressively higher further away. Note that the results in `trave_time_singapore` include infinite values (`Inf` above). In @fig-data, the islands to the south and north-east are shown as filled cells, but unconnected with the mainland. The raster cells for these islands appear absent in @fig-result. Because they are not connected to any cells with a station, the calculated travel time is infinite, and so these cells do not appear in @fig-result.

@@

The package associated with this paper contains information from the dataset "LTA MRT Station Exit (GEOJSON)" accessed on the 10th of December 2024 from  data.gov.sg, which is made available under the terms of the Singapore Open Data Licence version 1.0 https://data.gov.sg/open-data-licence.
